### 2016-06-17 Docs/FAQ/faq.tex
add note about GPROF=t

  An alternate way to get single-processor timings, when using 
  the GCC compilers is to add {\tt -pg} to the compilation flags
  for both {\tt gfortran} and {\tt gcc}.  Upon completion, a
  file names {\tt gmon.out} will be produced.  This can be 
  processed by {\tt gprof} running

>>>>

  An alternate way to get single-processor timings, when using the GCC
  compilers is to add {\tt -pg} to the compilation flags for both {\tt
    gfortran} and {\tt gcc} (this can be accomplished by setting {\tt
    GPROF := t} in your {\tt GNUmakefile}.  Upon completion, a file
  names {\tt gmon.out} will be produced.  This can be processed by
  {\tt gprof} running
